Multilevel regression models

### 2025-10-06 processing/03_prod_main_analysis.Rmd
images
better image quality

ggsave(plot = last_plot(),filename = "figure002.png",device = "png",
       path = here::here("output/images"),width = 2,height = 1,units = "cm",scale = 15)
```

```{r fig3, fig.dim=c(10,5),fig.cap='Cross-country differences in network homogeneity by social class ',warning=FALSE}
df_plot3 %>%
ggplot()+
  geom_point(aes(x = reorder(country3, diff_working_upper),
                 y = homclass,
                 shape=dclass3res_V,
                 color=dclass3res_V),
             size=3, alpha=2) +
  geom_hline(yintercept = mean(dfreg$homclass3_V_res),linetype=2)+
  scale_shape_manual(values = c(4,17, 15, 16)) +
  scale_color_manual(values = c("black","#000000","#666666","#999999")) +
  scale_y_continuous(limits = c(0,0.7))+
  labs(x=NULL,y="Network homogeneity",caption="Source: International Social Survey 2017; descriptive statistics; figure report country averages in network homogeneity by social class") +
  theme(legend.position = "bottom",
        legend.direction = "horizontal",
        axis.text.x=element_text(angle=45,hjust = 1,size=8),
        legend.title = element_blank())  
ggsave(plot = last_plot(),filename = "figure003.png",device = "png",
       path = here::here("output/images"),width = 2,height = 1,units = "cm",scale = 15)
```

@@

set.seed(1234)
ggsave(plot = arrangeGrob(fig_homo_gini,fig_egal_homo,
                          fig_homodiff_gini,fig_homodiff_redist,
             nrow = 2, 
 bottom =textGrob("Source: International Social Survey 2017; descriptive statistics; figure report country level pearson correlation; the line is the fitted values; CI at 95%",
 gp = gpar(fontface = 1, fontsize = 9),hjust = 1,x = 1
  )),
 filename = "figure004.png",device = "png",
 path = here::here("output/images"),width = 1,height = 1,units = "cm",scale = 26)
```

@@

## Model -  EGP3 - DIGCLASS - V to Working -----------------------------$ 
digclas1_VW_0<- lmer(egal~1 + dclass3res_V + female+agenum+know_total+(1|country2),data=dfreg,weights = WEIGHT)
# digclas1_VW_1<- lmer(egal~1 + homclass3_V_res+know_total +female+agenum+(1|country2),data=dfreg,weights = WEIGHT)
# digclas1_VW_2<- update(digclas1_VW_1, . ~ . +know_total) 
digclas1_VW_3 <- update(digclas1_VW_1, . ~ . + dclass3res_V)
# digclas1_VW_5 <- update(digclas1_VW_3, . ~ . + edyears+ Q03pcm+workst)

@@

ggsave(plot = last_plot(),filename = "figure005.png",device = "png",
       path = here::here("output/images"),width = 2,height = 1,units = "cm",scale = 15)
```

@@

ggsave(plot = last_plot(),filename = "figure006.png",device = "png",
       path = here::here("output/images"),width = 2,height = 1,units = "cm",scale = 15)
```

>>>>

ggsave(plot = last_plot(),filename = "figure002.png",device = "tiff",
       path = here::here("output/images"),width = 2,height = 1,units = "cm",scale = 15,dpi = 500)
```

```{r fig3, fig.dim=c(10,5),fig.cap='Cross-country differences in network homogeneity by social class ',warning=FALSE}
df_plot3 %>%
ggplot()+
  geom_point(aes(x = reorder(country3, diff_working_upper),
                 y = homclass,
                 shape=dclass3res_V,
                 color=dclass3res_V),
             size=3, alpha=2) +
  geom_hline(yintercept = mean(dfreg$homclass3_V_res),linetype=2)+
  scale_shape_manual(values = c(4,17, 15, 16)) +
  scale_color_manual(values = c("black","#000000","#666666","#999999")) +
  scale_y_continuous(limits = c(0,0.7))+
  labs(x=NULL,y="Network homogeneity",caption="Source: International Social Survey 2017; descriptive statistics; figure report country averages in network homogeneity by social class") +
  theme(legend.position = "bottom",
        legend.direction = "horizontal",
        axis.text.x=element_text(angle=45,hjust = 1,size=8),
        legend.title = element_blank())  
ggsave(plot = last_plot(),filename = "figure003.png",device = "tiff",
       path = here::here("output/images"),width = 2,height = 1,units = "cm",scale = 15,dpi = 500)
```

@@

set.seed(1234)
ggsave(plot = arrangeGrob(fig_homo_gini,fig_egal_homo,
                          fig_homodiff_gini,fig_homodiff_redist,
             nrow = 2, 
 bottom =textGrob("Source: International Social Survey 2017; descriptive statistics; figure report country level pearson correlation; the line is the fitted values; CI at 95%",
 gp = gpar(fontface = 1, fontsize = 9),hjust = 1,x = 1
  )),
 filename = "figure004.png",device = "tiff",
 path = here::here("output/images"),width = 1,height = 1,units = "cm",scale = 26,dpi = 500)
```

@@

## Model -  EGP3 - DIGCLASS - V to Working -----------------------------$ 
digclas1_VW_0<- lmer(egal~1 + dclass3res_V + female+agenum+know_total+(1|country2),data=dfreg,weights = WEIGHT)
# digclas1_VW_1<- lmer(egal~1 + homclass3_V_res+know_total +female+agenum+(1|country2),data=dfreg,weights = WEIGHT)
# digclas1_VW_2<- update(digclas1_VW_1, . ~ . +know_total) 
digclas1_VW_3 <- update(digclas1_VW_0, . ~ . + dclass3res_V)
# digclas1_VW_5 <- update(digclas1_VW_3, . ~ . + edyears+ Q03pcm+workst)

@@

ggsave(plot = last_plot(),filename = "figure005.png",device = "tiff",
       path = here::here("output/images"),width = 2,height = 1,units = "cm",scale = 15,dpi = 500)
```

@@

ggsave(plot = last_plot(),filename = "figure006.png",device = "tiff",
       path = here::here("output/images"),width = 2,height = 1,units = "cm",scale = 15,dpi = 500)
```
